---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# templateRpackage

<!-- badges: start -->
[![Project Status: WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![LifeCycle](https://img.shields.io/badge/lifecycle-experimental-orange)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- [![Dependencies](https://img.shields.io/badge/dependencies-0/0-brightgreen?style=flat)](#) -->
[![R CMD Check](https://github.com/Pakillo/templateRpackage/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Pakillo/templateRpackage/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Pakillo/templateRpackage/graph/badge.svg)](https://app.codecov.io/gh/Pakillo/templateRpackage)
[![Website](https://github.com/Pakillo/templateRpackage/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/Pakillo/templateRpackage/actions/workflows/pkgdown.yaml)
<!-- badges: end -->

## Overview

The goal of templateRpackage is to ...

## Installation

You can install the development version of templateRpackage from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("Pakillo/templateRpackage")
```

or

``` r
# install.packages("pak")
pak::pak("Pakillo/templateRpackage")
```

## Usage

```{r example}
library(templateRpackage)
```



## Citation

Please cite `templateRpackage` as: 

```{r results='asis'}
citation("templateRpackage")
```


## Contributing

All types of contributions are encouraged and valued. For more information, check out our [Contributor Guidelines](https://github.com/{{github_account}}/templateRpackage/blob/main/CONTRIBUTING.md).

Please note that the `templateRpackage` project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.




